---
title: "NYC Airbnnb Popularity Factors"
author: "Team World"
date: "10/24/2019"
output: github_document
---

### Section 1. Introduction

Using the Airbnb dataset, we hope to gain a better understanding of the gig hospitality market in New York City for 2019. Specifically, we want to find, explore and understand trends in the market as they relate to supply (availability) and demand (what people are willing to pay). The data set we chose allows us to draw conclusions and understand the factors that contribute to the New York City Airbnb scene. 

Through Kaggle, we found this data set (https://www.kaggle.com/dgomonov/new-york-city-airbnb-open-data) that was collected, and continues to be updated, in 2019 on Airbnb listings in New York City. This data set continues to be curated by a 4th year data science student at Drexel University (Dgomonov). We are unable to reach out to him to get more information on the data set, such as where he got it from or how he collected it, because our account on Kaggle is not at the "Contributor tier." 

To analyze this data set it is first important to understand its variables which include: listing ID, name of the listing, host ID, name of the host, location, neighbourhood, latitude and longitude coordinates, room type, price in dollars, minimum_nights, number of reviews, latest review, number of reviews per month, amount of listing per host and availability. A description of each of these is included in the codebook. 

Based on these factors, it seems as though price and availibility would make the most interesting response variables because they are very important to understand the economic landscape. For example someone who is looking to book an Airbnb is going to be very interested in what is available within their budget. Of course there are going to be other factors that are important to a consumer, such as location within NYC. However, we expect availability and price to be the most predictive and representative of the Airbnbs in New York City.

Some variables from the dataset that would be interesting to explore in section two that pertain to location include the borough, neighborhood, latitude, and longitude. We know that in real estate location highly influences value, especially in a large, wealthy, productive city like New York. We hope to explore how location influences potential response variables such as availability and price.

We also hope to explore how the listing is presented on the Airbnb platform might influence consumer choices. Some variables that could be insightful include the name of the listing which we may use text analysis to analyze. Each observation is also classified as one of three room types: private room, shared room and entire home/apt. Moreover, minimum nights required to stay and frequency of reviews are also included. We hope to see how this mix of categorical and numerical values impact one of the potential response variables. 

Although section two is preliminary exploration, various tools from the course such as the group_by function, the summarise function, linear modeling, and possible joining with outside data to draw meaningful insights. Clear and specific notation will be employed to make sure analysis is reproducible.

### Section 2. Exploratory data analysis

### Load packages & data

Loaded the tidyverse and broom packages:

```{r load-packages, message=FALSE}
library(tidyverse) 
library(broom)
```

Uploaded the Airbnb data set from Kaggle via a csv file:

```{r load-data, message=FALSE}
abnb <- read_csv("AB_NYC_2019.csv")
```

LOCATION AND PRICE:

Univariate Borough Count (Visualization):
Creating a histogram that displays number of listings by neighborhood borough in New York City.

```{r visualization-univariate}
ggplot(data = abnb, mapping = aes(x = neighbourhood_group)) +
  geom_histogram(stat = "count") + 
  labs(title = "Listings by Borough", x = "Borough", y = "Count")
```

According to this histogram, Manhattan and Brooklyn dominate the number of listings on Airbnb in New York City. More specifically, there is roughly 20,000 listings in Brooklyn and slightly more than 20,000 listings in Manhattan. The Queens borough follows after with roughly 5,000 listings, followed by Bronx and Staten Island with fewer than 1,100 listings each.

Univariate Borough Count (Summary)
Creating summary statistics that will count the number of listings in each neighborhood group.
```{r neighbourhood_group-count}
abnb %>%
  count(neighbourhood_group) %>%
  arrange(desc(n))
```

According to the table, Manhattan has the most listings at 21,661 followed by Brooklyn at 20,104 listings, followed by Queens at 5,666, Bronx at 1,091, and Staten Island last at only 373 listings.


Creating a facet histogram that will display the price of listings by borough.

```{r price-borough}
abnb %>%
  ggplot(mapping = aes(x = price)) +
  geom_histogram(bins=35) +
  facet_wrap(.~neighbourhood_group)
  labs(title = "Price of Listings by Borough", x = "Borough", y = "Price")
```

The graphs display that the prices for listings are very skewed to the right. In other words, there are many outliers that fall out of the IQR for each neighborhood group. Most listings fall in the 50 to 150 price range. However, there are outliers that are a lot higher than this price range.


Creating summary statistics that displays the median and IQR price of each neighborhood group.

```{r summarise-price}
abnb %>%
  group_by(neighbourhood_group) %>%
  summarise(
    med_price = median(price), 
    IQR_price = IQR(price)
    ) %>%
  arrange(desc(med_price)) %>%
  head(5)
```

According to the table, Manhattan has the highest median price at 150 followed by Brooklyn at 90, Queens and Staten Island at 75, and Bronx last at 65. 

Creating summary statistics that finds the median price based upon neighborhood in descending order.

```{r neighbourhood_group-neighbourhood}
abnb %>%
  group_by(neighbourhood_group, neighbourhood) %>%
  summarise(median_price = median(price)) %>%
  arrange(desc(median_price)) %>%
  head(5)
```

According to the table, Fort Wadsworth in Staten Island has the highest median price at 800 followed by Woodrow at 700, Tribeca at 295, Neponsit at 274, and NoHo at 250.

```{r price-at-longtitude}
abnb %>%
  ggplot(mapping = aes (x = longitude, y = latitude, color = price)) +
  geom_point(alpha = 0.6)
```

The graph displays that most listings take place in the (-74, -73.7) longtitude region and (40.55, 40.9) latitude region. Prices are generally in the 50 to 150 range.

LISTING DETAILS AND AVAILABILITY


```{r avail-listings-distr, message=FALSE}
abnb %>%
  ggplot(mapping = aes(x = availability_365)) +
  geom_histogram(binwidth=80) + 
  labs(title = "Availability of Listings Distribution",
       x = "Availability (days per year)",
       y = "Count"
  )
```

The graph is skewed to the right with most occurrences happening in the 0 to 100 availibily (days per year). More specifically, approximately more than 25,000 listings occurr in the 0 to 100 availability (days per year).

```{r room_type-availability_365, message=FALSE}
abnb %>%
  ggplot(mapping = aes(x =  room_type, y = availability_365)) +
  geom_boxplot() + 
  labs(
    title = "Availability by Room Type",
    x = "Room Type", 
    y = "Availability (days per year)")
```

The graph above are boxplots that show that the availability based on room type is also skewed to the right. The median availability days among entire home and private rooms are slightly less than 50 days while shared rooms have a rough median availability of 90 days.

```{r table-avail}
abnb %>%
  group_by(room_type) %>%
  summarise(
    med_availability_365 = median(availability_365), 
    IQR_availability_365 = IQR(availability_365)
    ) %>%
  arrange(desc(med_availability_365)) %>%
  head(5)
```

The table shows that the median availability are 90 days for shared room, 45 days for private room, and 42 days for entire home/apartment.


```{r prop-of-avail}
abnb %>%
  mutate(avail = case_when(
    availability_365 < 100            ~ "Very Busy",
    availability_365 < 200 && availability_365 > 100  ~ "Somewhat Busy",
    availability_365 > 300    ~ "Not Busy",)
    ) %>%
ggplot(mapping = aes(x = room_type, fill = avail)) +
  geom_bar(position = "fill")
```

The stacked bar graph above shows the proprotion of listings based on room_type that are either not busy, very busy, or have no data (NAs).
According to the graph, all entire home, private rooms, shared room listing types are generally mostly very busy at roughly 60% while only roughly 20% across the charts are roughly not busy. Shared rooms are generally less busy than private rooms and entire home/apt listings.

```{r avail-by-room_type-reviews, message=FALSE}
abnb %>%
  mutate(avail = case_when(
    availability_365 < 100            ~ "Very Busy",
    availability_365 >= 100 & availability_365 <= 300  ~ "Somewhat Busy",
    availability_365 > 300    ~ "Not Busy",)
    ) %>%
ggplot(mapping = aes(x = calculated_host_listings_count, y = reviews_per_month)) +
  geom_point() +
  facet_grid(room_type ~ avail)
```

The graphs above show that among entire home/apt and private rooms, there is a higher amount of reviews per month (roughly less than 20) with fewer calculated host listings.

### Section 3. Research questions

The first research question that we are interested in exploring is “How does location (borough and neighborhood, for example) influence the price of a listing?”

Through our exploratory analysis we were able to see that the vast majority of Airbnb listings are located in Brooklyn and Manhattan which is not surprising. We are very interested in the prices of different Airbnb listings, we can see the distribution of prices for each borough in the second visualization. The highest median price is located in Manhattan at $150 as well as the largest IQR ($125). The histograms also show that for each borough, price is very dramatically skewed right with many outliers. 

We then decided to look further into price distribution across neighborhoods within each borough which showed the highest median price per neighborhood was Fort Wadsworth, Staten Island which was surprising because Staten Island overall had one of the lowest median prices. We plan to continue this analysis to determine what other factors contribute to fluctuation in prices (such as using latitude and longitude coordinates to see how distance from central park may affect prices as well as which neighborhoods are the highest and lowest cost relative to its borough). 

To complete this research we will use the location variables (neighbourhood, neighbourhood_group, and latitude longitude) as predictors variables and price will be the response variable.


How does the way in which a property is listed (type of room, for example) influence the availability of a listing?

### Section 4. Data

Used the glimpse function to show information about and part of abnb:

```{r glimpse}
glimpse(abnb)
```

