---
title: "NYC Airbnb Popularity Factors"
author: "WORLD"
date: "12/6/2019"
output: github_document
---

## Introduction: 

Every day, thousands of tourists visit the historic city of New York. It is one of the most populous city in the United States and is a popular attraction for tourists, not only from the United States but around the world. Given the popularity of tourists, the lodging and hotel industry has benefited tremendously. Airbnb is an online marketplace for arranging and offering homestays to thousands of tourists every day in the beloved city of New York. 

Through Kaggle, we found this data set (https://www.kaggle.com/dgomonov/new-york-city-airbnb-open-data) that was collected and continues to be updated through 2019 on Airbnb's in New York City. This data set continues to be curated by a 4th year data science student at Drexel University (Dgomonov). We are unable to reach out to him to get more information on the data set, such as where he got it from or how he collected it, because our account on Kaggle is not at the "Contributor tier." However, we can reasonably infer that the dataset was created by web scraping Airbnb’s website. Moreover, since the dataset is looking at all the listings in NYC, we are assuming that the dataset is indicative of a population. Therefore, we have created a sample dataset for our data analysis.

To analyze this data set, it is first important to understand its variables: listing ID, name of the listing, host ID, the name of the host, location, neighbourhood, latitude, longitude, room type, price in dollars, minimum nights, number of reviews, date of latest review, number of reviews per month, amount of listings per host, and availability. 

Based on these factors, it seems as though price and availability would make the most interesting response variables because they are very important to understand the economic landscape. For example, someone who is looking to book an Airbnb is going to be very interested in what is available within their budget. Of course, there are going to be other factors that are important to a consumer, such as location within NYC. However, we expect availability and price to be the most predictive and representative of the Airbnbs in New York City.

Our central focus will be on predicting, analyzing, and performing tests on the price and availability of Airbnb listings. For our final project, we want to answer two major research questions: How does location influence the price of Airbnb listings and how does the way in which an Airbnb is described influence availibility in New York City?

Using the Airbnb dataset, we hope to gain a better understanding of the gig hospitality market in New York City for 2019. Specifically, we want to find, explore and understand trends in the market as they relate to supply (availability) and demand (what people are willing to pay). The data set we chose allows us to draw conclusions and understand the factors that contribute to the New York City Airbnb scene.

The dimensions and codebook are below:

### Dimensions:

`Observations: 48,895` 

`Variables: 16`

### Codebook:

`Variable Name                  --> Description`

`id                             --> The specific listing's ID value from the Airbnb website.` 

`name                           --> Host-produced description of the listing.`

`host_id                        --> The ID unique for the listing's owner.`

`host_name                      --> First name of host/hosts.`

`neighbourhood_group            --> One of the NYC five boroughs (Manhattan, Brooklyn, Queens, Staten Island, The Bronx)`

`neighbourhood                  --> Specific area within each of the boroughs.`

`latitude                       --> Horizontal global coordinate.`

`longitude                      --> Vertical global coordinate.`

`room_type                      --> One of three classifications (Etire home/apartment, Private Room, or Shared Room).`

`price                          --> The listing's price in United States dollars per night.`

`minimum_nights                 --> The minimum nights required by the host to stay.`

`number_of_reviews              --> Quantity of online reviews given for a listing.`

`last_review                    --> Year/Month/Date of the most recent review.`

`reviews_per_month              --> Quantity of reviews on average in a given month.`

`calculated_host_listings_count --> Number of listings per one host.`

`availability_365               --> Quantity of days in which the listing is available.`


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-packages, message=FALSE}
library(tidyverse) 
library(infer)
library(openintro)
library(dplyr)
library(knitr)
library(broom)
library(tidytext)
```

```{r load-data, message=FALSE}
abnb <- read_csv("AB_NYC_2019.csv")
```

In order to perform analysis, we created a sample set of 4000 randomly selected observations. The following analysis and conclusions are drawn from that sample set.

```{r abnb_sample}
set.seed(111519)
abnb_sample <- sample_n(abnb, 4000)
```

## Part I: Price and Location

For our first research question, we hope to explore how location influences the price as a response variable. Some variables from the dataset that pertains to price and would be interesting to explore are borough, neighborhood, latitude, and longitude. We know that in real estate location highly influences the value  of properties and rent rates, especially in a large, wealthy, productive city like New York. Thus, we believe that this would likely have a relationship with price.

In part I, the following research question will be examined: How does location (borough and co-ordinates, for example) influence the price of a listing?

### Understanding Price

To start, a bootstrap distribution and 95% bootstrap confidence interval was constructed for the median price of Airbnbs in NYC. This will help to better understand the range of prices and the real estate landscape that the true median price would be within. 

```{r boot-med_price}
set.seed(111519)
boot_dist_median_price <- abnb_sample %>%
  specify(response = price) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "median")
```

```{r boot_dist_median_priceci}
(ci_bounds <- get_ci(boot_dist_median_price, level= 0.95))
```

A visualization of the bootstrap distribution for median price is depicted below:

```{r boot_dist_median_visu}
visualize(boot_dist_median_price) + 
  labs(title = "Bootstrap Distribution of Median Price") +
  shade_ci(ci_bounds)
```

We are 95% confident that the population median price per night of Airbnbs in NYC is between $100.00 and $110.00. This information will help us understand prices in the Airbnb market as we go about attempting to draw comparisions.

### Exploring Boroughs

The first location variable that might be helpful to explore is borough given that New York City is divided into five areas (The Bronx, Brooklyn, Manhattan, Queens, and Staten Island).

Next for exploratory data analysis, a bar graph that displays number of listings by borough in New York City is shown below:

```{r visualization-univariate}
ggplot(data = abnb, mapping = aes(x = neighbourhood_group)) +
  geom_bar() + 
  labs(title = "Listings by Borough", x = "Borough", y = "Count")
```

Manhattan and Brooklyn dominate the number of listings on Airbnb in New York City. More specifically, there is roughly 20,000 listings in Brooklyn and slightly more than 20,000 listings in Manhattan. Queens follows after with roughly 5,000 listings, followed by the Bronx and Staten Island with fewer than 1,100 listings each. A summary statistic is calculated below to get the exact count of listings.

```{r neighbourhood_group-count}
abnb %>%
  count(neighbourhood_group) %>%
  arrange(desc(n))
```

Manhattan has the most listings at 21,661 followed by Brooklyn at 20,104 listings, followed by Queens at 5,666, Bronx at 1,091, and Staten Island last at only 373 listings.

```{r summarise-price}
abnb %>%
  group_by(neighbourhood_group) %>%
  summarise(med_price = median(price)) %>%
  arrange(desc(med_price)) %>%
  head(5)
```
Now, when looking at median price by borough, Manhattan has the highest median price at 150 followed by Brooklyn at 90, Queens and Staten Island at 75, and the Bronx last at 65. 

It is clear that quantity of listings as well as median price varies greatly across each of the five boroughs. After further exploration of the relevant location variables we will predict how much these variables influence price by developing a linear model.

First we would like to visualize the distribution of price by borough, below is a boxplot to show price by borough.

```{r price_box_neighbourhood_group, message=FALSE}
abnb_sample %>%
  ggplot(mapping = aes(x = neighbourhood_group, y = price, fill = neighbourhood_group)) +
  geom_boxplot() + 
  labs(
    title = "Price by Borough",
    x = "Borough", 
    y = "Price (per night)")
```

The boxplot above shows the price of renting an Airbnb per night based on the borough that the Airbnb is located in. Due to extremely right skewed data and very expensive outliers this box plot does not display the actual distribution as well as we hoped. In order to make a more useful visualization, we filtered for price below $1000.00 and recreated the box plot below.

```{r filtering_resid}
abnb_sample_filter <- abnb_sample %>%
  filter(price <= 1000)
```

```{r price_box_neighbourhood_group_filter, message=FALSE}
abnb_sample_filter %>%
  ggplot(mapping = aes(x = neighbourhood_group, y = price, fill = neighbourhood_group)) +
  geom_boxplot() + 
  labs(
    title = "Price by Borough",
    x = "Borough", 
    y = "Price (per night)")
```

We have already found above, that Manhattan has the highest median price, followed by Brooklyn, Queens and Staten Island, and finally the Bronx has the lowest median available price for Airbnb's in Manhattan per night. What we did not know that is evident in both the original and the above graph is that Manhattan and Queens have the largest ouliers (Manhattan's largest outlier stands at >$8,000 per night and Queen's is about $2,000 per night). Staten Island has the lowest IQR and Manhattan has the largerst IQR, this is not surprising considering the number of listings that we found above, Manhattan with 21,661 vs Staten Island with only 373. 

### Visualizing Manhattan

From the previous sections, it has become clear that Manhattan is the most expensive borough for Airbnbs. In order to confirm this visually, we will create a scatterplot. To simplify the scatterplot, price will be broken down into two catergories based on the median price of all Airbnbs in NYC. In order to do this we create and use a new variable (price_case) which describes whether the price of the listing is at or above the median price or below the median price. A visualization of Airbnbs by latidude and longitude co-ordinates and using color to distinguish between the price types is shown below.

```{r median_price-mutate}
abnb_sample <- abnb_sample %>%
   mutate(price_median = median(price), 
          price_case = case_when(
      price >= price_median ~ "Median or Above",
      price < price_median ~ "Below Median", 
    ))
```

```{r price-at-location}
abnb_sample %>%
  ggplot(mapping = aes (x = longitude, 
                        y = latitude, 
                        color = price_case)) +
  geom_jitter(alpha = 0.5) +
  labs(title = "Prices at Latitude and Longitude Coordinates", 
       x = "Longitude", 
       y = "Latitude", 
       color = "Price Case")
```

It is clear from this map, that the cases in which the prices are at the median or above (blue dots) are clustered around Manhattan. Therefore, visualization once again confirms our previous findings. The area that appears to have the second most number of blue dots is Brooklyn, which is right next to Manhattan. We determined the relative frequency of listings that are above or at the median price by borough and found Manhattan has the greatest frequency. of median or above listings at 68.757%, followed by Brooklyn at 40.380%. Queens has 24.448%, Staten Island has 21.739% and the Bronx has 15.294%.

```{r boroughs-rel_freq}
abnb_sample %>%
  count(neighbourhood_group, price_case) %>%
  group_by(neighbourhood_group) %>%
  mutate(rel_freq = n/sum(n)) %>%
  filter(price_case == "Median or Above") %>%
  arrange(desc(rel_freq))
```

Manhattan has the greatest frequency of median or above listings at 68.757%, followed by Brooklyn at 40.380%. Queens has 24.448%, Staten Island has 21.739% and the Bronx has 15.294%.

### Neighborhood?

After discovering the vairation in price between borough, we were very interested in exploring how price was affected by neighbourhood (within each borough). We calculated the median price of the top 10 neighborhoods and checked their corresponding borough to see if they tend to lie in same borough, which we might expect to be Manhattan as it is the most expensive borough.

```{r med-price-neighborhood}
abnb_sample %>%
  group_by(neighbourhood, neighbourhood_group) %>%
  summarise(med_price = median(price)) %>%
  arrange(desc(med_price)) %>%
  head(10)
```

The neighborhoods with the most expensive Airbnbs come from a range of boroughs. In fact, all are represented in the top 10 equally. Surprisingly, the Bronx contains the neighborhood, Eastchester, with the highest median price of $475.00. Given the extensive analysis already done for location by borough and co-ordinates, neighborhood will not be analyzed further as it is beyond the initial scope of our focus. 

### Regression analysis

As stated above, we would like to predict how much these location variables influence price. To do this we develop a linear model to describe how boroughs influence price and, since Manhattan had the largest volume of Airbnbs and the highest median price, that will be the baseline for comparison with other boroughs.

```{r mutate-neighbourhood_group}
abnb_sample <- abnb_sample %>%
  mutate(neighbourhood_group = fct_relevel(neighbourhood_group, 
                                           "Manhattan", 
                                           "Brooklyn",
                                           "Staten Island",
                                           "Queens",
                                           "Bronx"))
```

When creating a linear model to predict Airbnb price by borough. It is first important to discuss the assumptions we are making when performing this regression. We are assuming each listing is independent because the pricing of one space does not driectly influence the other. While some might argue there is dependence between listings to some extent, the market for Airbnbs in NYC is free and competitive so renters, ideally, don't collude.

```{r lm-price-borough}
lm_price_borough <- lm(price ~ neighbourhood_group, data = abnb_sample)
```

In addition to independence, there are other assumptions that need to be discussed. Thus, a residuals plot is shown below:

```{r lm_price_borough_aug-residuals}
lm_price_borough_aug <- augment(lm_price_borough)
ggplot(data = lm_price_borough_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, lty = 3, color = "gray") +
  labs(y = "Residuals", 
       x = "Predicted values, y-hat", 
       title = "Residual Plot")
```

As the predicted values increase, the spread of the residuals increase in a "fan" like shape. This violates the constant variance assumption needed for regression. Therefore, we will proceed with caution when drawing assumptions from the linear regression.

As depicted in the normality of residuals graph below, the residuals are randomly distributed around 0. 

```{r lm_price_borough_aug-nomalities}
ggplot(data = lm_price_borough_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 300) +
  labs(x = "Residuals", 
       title = "Normality of Residuals")
```

However, the residuals are not nearly normally distributed. Therefore, we will filter out outliers to get a residuals graph that has a nearly normal distribution.

```{r lm_price_borough_aug-nomality-filtered}

lm_price_borough_aug_filter <- lm_price_borough_aug %>%
  filter(.resid <= 250 & .resid >= -170 )

ggplot(data = lm_price_borough_aug_filter, aes(x = .resid)) +
  geom_histogram(binwidth = 100) +
  labs(x = "Residuals", 
       title = "Filtered Normality of Residuals")
```

```{r lm-price-borough-output}
lm_price_borough %>% 
  tidy() %>% 
  select(term, estimate, p.value) %>%
  kable(format = "markdown", digits =3)

```

The linear model that describes how boroughs influence price:

`price-hat = 206.848 -85.106*(neighbourhood_groupBrooklyn) -117.674*(neighbourhood_groupStaten Island) -110.432*(neighbourhood_groupQueens) -126.213(neighbourhood_groupBronx)`

Given that the Airbnb is in Manhattan, the expected median price, on average, is $206.85. In this case, the intercept does have a meaningful interpretation because an Airbnb could have a price of $206.85 per night.

The median price for the other boroughs in relation in Manhattan is:

For an Airbnb in Brooklyn, the median price is expected, on average, to be $85.11 less than an Airbnb in Manhattan, holding all else constant.

For an Airbnb in Staten Island, the median price is expected, on average, to be $117.67 less than an Airbnb in Manhattan, holding all else constant.

For an Airbnb in Queens, the median price is expected, on average, to be $110.43 less than an Airbnb in Manhattan, holding all else constant.

For an Airbnb in Bronx, the median price is expected, on average, to be $126.21 less than an Airbnb in Manhattan, holding all else constant.

We have confirmed that all the p-values are less than the threshold of 0.05; therefore, the expected median prices predicted by the regression model are significant.

```{r rsqaure-lm_price_borough}
glance(lm_price_borough)$r.squared
```

The R squared of the linear model is .0367. Thus, roughly 3.670% of the variability in median price can be explained by the borough.

### Comparing Manhattan and Brooklyn

We are suspicious that there might be a relationship between median price in Manhattan and Brooklyn because they contain the largest amount and the most expensive Airbnbs. Also, the linear model above showed that the expected difference of $85.11 in median price was the least between Brooklyn and Manhattan and the p-value was less than 0.05. Therefore, we will attempt to answer the following: Is there is a significant difference in the true median prices between Manhattan and Brooklyn? The observed difference in median prices was calculated.

```{r filter-borough}
abnb_sample_filtered <- abnb_sample %>%
  filter(neighbourhood_group == "Manhattan" | neighbourhood_group == "Brooklyn")
```

```{r sample_diff_med}
abnb_sample_filtered %>%
  group_by(neighbourhood_group) %>%
  summarise(med_price = median(price))
```

The observed median prices for Manhattan and Brooklyn are $150.00 and $90.00, respectively. Therefore, the observed difference in median prices is $60.

With this observed difference a hypothesis test was conducted:

Null Hypothesis: There is no difference in median price between Manhattan and Brooklyn Airbnb per night.

Alternative Hypothesis: There is a difference in median price between Manhattan and Brooklyn Airbnb per night.

```{r man-brook-med-price}
set.seed(111519)
null_dist_man_brook_med_price <- abnb_sample_filtered %>%
  specify(response = price, explanatory = neighbourhood_group) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("Manhattan", "Brooklyn"))

```

Below is a visualization of the null distribution:

```{r null_dist_diff_median_vis, warning=FALSE}
visualize(null_dist_man_brook_med_price) + 
  labs(title = "Null Dist of Difference in Median Price between Manhattan and Brooklyn") +
  shade_p_value(obs_stat = 60, direction = "two_sided")
```

From the visualization, there appears to be no overlap between the shaded region and the null distribution. 

```{r null_dist_diff_median_p_val}
get_p_value(null_dist_man_brook_med_price, 60, direction = "two_sided")
```

To confirm what is clear in the visualization we found the p-value. As expected, the p-value is 0, which is less than the significance value of 0.05. Therefore, we reject the null hypothesis that there is no difference in median price between Manhattan and Brooklyn Airbnb per night. We conclude that the data does provide convincing evidence of a difference in median price of Airbnbs for listings in Manhattan and Brooklyn.

Next we create a bootstrap distribution and 95% confidence interval of the difference in median prices between listings in Manhattan and Brooklyn. 

```{r boot-man-brook-medprice}
boot_man_brook_medprice <- abnb_sample_filtered %>%
  specify(response = price, explanatory = neighbourhood_group) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in medians", c("Manhattan", "Brooklyn"))
```
```{r ci-boot}
(ci_bounds2 <- get_ci(boot_man_brook_medprice, level = 0.95))
```

To conclude we are 95% confident that the median price in Manhattan is between $55 and $65 higher than the median price in Brooklyn. 

 

## Part II: Availability and Property Listing

In part II, the following research question will be examined: How does the way in which a property is listed influence the availability of a listing? The the variables that are relevant in how the listing is presented include the name of the listing, room type, minimum number of nights and calculated number of listings by  host. These are variables that might inform consumer choices and be indicative of the number of available days of a listing.


### Understanding Availability

To start, a bootstrap distribution and 95% bootstrap confidence interval was constructed for the median number of available days of an Airbnb. This will help to better understand the range of available number of days (out of 365) and the market demand.

```{r avail_boot_distribution}
set.seed(111519)
boot_dist_avail <- abnb_sample %>%
  specify(response = availability_365) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "median")
```

```{r boot_dist_availability_365}
(ci_bounds <- get_ci(boot_dist_avail, level= 0.95))
```

We are 95% confident that the median number of available days of Airbnbs in New York City is between 42 and 57 days. This information will help us understand availability in the Airbnb market as we go about attempting to draw comparisions. A visualization of the bootstrap distribution and 95% confidence interval for median availability is shown below:

```{r visualize_avail365}
visualize(boot_dist_avail) + 
  labs(title = "Bootstrap Dist of Median Number of Available Days of Airbnbs in NYC") +
  shade_ci(ci_bounds)
```

### Descriptions and Desires: What makes an Airbnb appealing?

In order to work with availability further, we categorize it in terms of ranges. Those available less than or equal to 73 days are "low", those greater than 73 and less than or equal to 143 are "medium low", those greater than 143 and less than or equal to 219 are "medium", those greater than 219 and less than or equal to 292 are "medium high", and those greater than 292 are "high".

```{r avail-catergory}
abnb_sample <- abnb_sample %>%
  mutate(availability_365_case = case_when(
      availability_365 <= 73  ~ "Low",
      availability_365 <= 143 & availability_365 > 73 ~ "Medium Low",
      availability_365 > 143 & availability_365 <= 219 ~ "Medium",
      availability_365 > 219 & availability_365 <= 292 ~ "Medium High",
      availability_365 > 292 ~ "High", 
    ))
```

Another important factor of the way a given Airbnb is listed is the description (name) written by the host. We are interested in how descriptions could influence which Airbnbs are most popular. Given that the descriptions of an Airbnb listings include multiple words or short sentences, text analysis is be performed. 

```{r abnb_text}
abnb_text <- abnb_sample %>%
  select(id, name, availability_365_case, availability_365)
```

```{r text-analysis}
remove_reg <- "&amp;|&lt;|&gt;"
tidy_description <- abnb_text %>%
  mutate(name = str_remove_all(name, remove_reg)) %>%
  unnest_tokens(word, name)
```

```{r words-common}
tidy_description <- tidy_description %>%
  filter(!word %in% stop_words $ word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]"))

tidy_description %>%
  count(word, availability_365, sort = T) %>%
  arrange(availability_365) %>%
  head(10)
```

After removing stop words, the top most common words used in descriptions of significance for Airbnb listings with the least availability are bedroom, apartment and private. 

A visualization of the relaitve frequency of the top 10 most common words is shown below: 

```{r word-freq-vis}
frequency_all <- tidy_description %>%
  count(word, sort = T) %>%
  mutate(freq = n / sum(n)) 

ggplot(frequency_all %>% top_n(10, freq) %>%
         mutate(word = reorder(word, freq)), aes(x = word, y = freq))+
  geom_col()+ 
  coord_flip()
```

It appears that the word bedroom was an appeal for many bookers likely because it gives a sense of exclusivity and privacy, which many people look for while travelling. Moreover, the second most common word, private, underscores this desire. Additionally, the considering we are looking at NYC, the word apartment would be descriptive of a private enclave within the hustle and bustle of one of the busiest cities in the world. 

Source for text analysis: https://www.tidytextmining.com/tidytext.html

### Physical Description

It seems as though how the physical description of the room influences the number of booking and thus, the availability of the listing. Therefore, we will create a linear model to predict Airbnb availability by roomtype.  

In order to find the baseline, we will use our exploratory analysis. The boxplot below shows which room type (shared, private or house/apartment) is available for the most amount of days per year:

```{r room_type-availability_365, message=FALSE}
abnb %>%
  ggplot(mapping = aes(x =  room_type, 
                       y = availability_365, 
                       fill = room_type)) +
  geom_boxplot() + labs(
    title = "Availability by Room Type",
    x = "Room Type", 
    y = "Availability (days per year)")
```

The graph above are boxplots that show that the availability based on room type is also skewed to the right. The median available number of days days among entire home and private rooms are slightly less than 50 days while shared rooms have a rough median availability of 90 days. Shared rooms are available for the most number of days in the year. 

Summary statistics for availibility by room type:

```{r table-avail}
abnb %>%
  group_by(room_type) %>%
  summarise(
    med_availability_365 = median(availability_365), 
    IQR_availability_365 = IQR(availability_365)
    ) %>%
  arrange(desc(med_availability_365))
```

The median availability are 90 days for shared room, 45 days for private room, and 42 days for entire home/apartment. The range for shared room type is the highest with 341 days.

Therefore, entire home/apt will be our baseline for the linear model to show the influence of room type on availability.

```{r lm-avail-room-type}
lm_avail_room_type <- lm(availability_365 ~ room_type, data = abnb_sample)
```

It is first important to discuss the assumptions we are making when performing this regression. We are assuming each room type is independent because the availability of one room type doesn't affect the availability of another room type.

In addition to independence, there are other assumptions that need to be discussed. Thus, a residuals plot is shown below:

```{r lm_avail_borough_aug}
lm_avail_room_type_aug <- augment(lm_avail_room_type)
ggplot(data = lm_avail_room_type_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, lty = 3, color = "gray") +
  labs(y = "Residuals", 
       x = "Predicted values, y-hat", 
       title = "Residual Plot")
```

As the predicted values increase, the spread of the residuals decreases. This violates the constant variance assumption needed for regression. Therefore, we will proceed with caution when drawing assumptions from the linear regression as there is non-randomness in the residual form.

As depicted in the normality of residuals graph below, the residuals are randomly distributed around 0 AND nearly normal. 

```{r lm_avail_borough_aug-nomality}
ggplot(data = lm_avail_room_type_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 300) +
  labs(x = "Residuals", 
       title = "Normality of Residuals")
```

```{r lm_avail_room_type-output}
lm_avail_room_type %>% 
  tidy() %>%
  select(term, estimate, p.value) %>%
  kable(format = "markdown", digits =3)

```

The linear model that describes the influence of room type on availability is:

`price-hat = 115.774 -3.443*(room_typePrivateroom) +74.912*(room_typeShared room)`

Given that the Airbnb has the roomtype of entire house/apt the expected median availability, on average, is 115.8 days out of the year. In this case, the intercept does have a meaningful interpretation because an Airbnb could be available for 115.8 days out of 365 per year.

The availability of the other room types in relation to entire home/apartment is: 

For an Airbnb with roomtype of private room, the median availability is expected, on average, to be 3.4 days less per year than an Airbnb in wth room type of entire house/apt, holding all else constant.

For an Airbnb with roomtype of shared room, the median availability is expected, on average, to be 74.9 days more per year than an Airbnb in wth room type of entire house/apt, holding all else constant.

We confirmed that all the p-values, except for private room, are less than the threshold of 0.05; therefore, the expected median availabilty predicted by the regression model for shared rooms is significant.

```{r rsqaure-lm_avail_room_typex}
glance(lm_avail_room_type)$r.squared
```

The R squared of the linear model is 0.00841. This means that roughly 0.841% of the variability in median availability can be explained by the type of room of Airbnb's in New York. This is a relatively small R squared value. Perhaps there are other factors which influence availability.

### Listing Factors and Availability

There are many other variables that we believe could affect the availibility of the listing. In order to look at these other factors, we will select a model using AIC backwards selection.

```{r remove-na}
abnb_model <- abnb_sample %>%
  drop_na(availability_365,
          room_type, minimum_nights, 
          number_of_reviews,
          calculated_host_listings_count, 
          price_case, 
          reviews_per_month)

m_full_model <- lm(availability_365 ~ room_type + 
                     minimum_nights +  
                     number_of_reviews + 
                     calculated_host_listings_count + 
                     price_case + 
                     reviews_per_month, data = abnb_model)
```

```{r AIC-backward-selection, results="hide"}
selected_model <- step(m_full_model, direction = "backward")
```

We created another linear model, this time to predict Airbnb availability by reviews per month, minimum number of nights, whether the price was at the median/above or not, the room type, number of reviews, and the calculated number of host listings. It is important to discuss the assumptions that we are making when performing this regression. We are assuming each of these factors is independent because they do not directly influence each other.

In addition to independence, there are other assumptions that need to be discussed such as constant variance. Therefore, a residuals plot is shown below:

```{r lm_price_borough_aug}
selected_model_aug <- augment(selected_model)
ggplot(data = selected_model_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, lty = 3, color = "gray") +
  labs(y = "Residuals", 
       x = "Predicted values, y-hat", 
       title = "Residual Plot")
```

As the predicted values increase, the spread of the residuals shifts downward. This violates the constant variance assumption needed for regression. Therefore, we will proceed with caution when drawing assumptions from the linear regression as there is non-randomness in the plot.

As depicted in the normality of residuals graph below, the residuals are randomly distributed around 0 AND nearly normal. 

```{r lm_price_borough_aug-nomality}
ggplot(data = lm_price_borough_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 300) +
  labs(x = "Residuals", 
       title = "Normality of Residuals")
```

```{r selected-kable}
tidy(selected_model) %>%
  select(term, estimate, p.value) %>%
  kable(format = "markdown", digits = 3)
```

The selected linear model to predict Airbnb availability by reviews per month, minimum number of nights, whether the price was at the median/above or not, the room type, number of reviews, and the calculated number of host listings is:

`availability_365 = 59.923 + 26.396*(room_typePrivate room) +115.98*(room_typeShared room) + 0.481*(minimum_nights) +0.461*(number_of_reviews) + 0.853*(calculated_host_listings_count) +29.622*(price_caseMedian or Above) + 5.93*(reviews_per_month)`

Categorical predictor:
Listings that are of room_type: Private room, are expected to have, on average, an average availibility of 26.396 higher than the average availability of listings that are of room_type: Whole house/APT, holding all else constant.

Numerical predictor:
With each additional number of minimum nights required to stay at the airbnb (minimum_nights), it is expected, on average, that availibility increases by 0.481 days, holding all else constant.

We confirmed, all the p-values are less than the threshold of 0.05; therefore, the expected median availabilities predicted by the regression model are significant.

```{r r-square-selectedmodel}
glance(selected_model)$r.squared
```

The R-squared value is 0.1049. This means 10.49% of the variability in availibility can be explained by the way the property is listed - the room type, minimum nights required, number of reviews the listing has, the number of listings the host has, the median price and the reviews per month. Compared to our other models, this is a relatively higher R squared value. It is also important to note that room types have high coefficients.

### Host Volume

The last thing we have to consider, is the number of listings the host holds. This is significant because whether a host hold multiple properties could influence the listing availability. Also, those with multiple properties could use Airbnb renting business as a consistent source of income. We define a host as "high volume" if they hold more than one listing and "low volume" if they hold only one listing. Thus, it provides us with more information about the owner of the Airbnb.

Moreover, we are trying to understand how the number of listings per host in NYC influence the availability. We believe this analysis could give us more insight into the type of hosts that use the Airbnb service. We hope to see how this mix of categorical and numerical values impacts one of the potential response variables. 

```{r remove-id}
abnb_sample <- abnb_sample %>%
  select(-(id))
```

```{r abnb_host_volume}
abnb_host_volume <- abnb_sample %>%
  count(host_id) %>%
  mutate(host_volume = if_else(n> 1, "high volume", "low volume"))
```

```{r inner-join}
abnb_host_volume <- abnb_host_volume %>%
  inner_join(abnb_sample, by = "host_id")
```

We found the number of high volume hosts and low volume hosts:

```{r num-volume}
abnb_host_volume %>%
  count(host_volume)
```

436 of the hosts are high volume and 3564 of the hosts are low volume.

Visualizing this in a bar graph:

```{r host-vol-graph}
abnb_host_volume %>%
  ggplot(mapping = aes(x = host_volume)) +
  geom_bar() +
  labs(title = "Type of Host vs. Count", 
       x = "Type of Host", y = "Count") 
```

Next, we decided to conduct a hypothesis test to see if availability can be explained depending on whether a host is high volume or not:

Ho: There is no difference in the median availability of high volume and low volume hosts.

Ha: There is a difference in the median availability of high volume and low volume hosts.

Finding observed median availability:

```{r obs-med-avail}
abnb_host_volume %>%
  group_by(host_volume) %>%
  summarise(medianavail = 
              median(availability_365))
```

The observed median availability of high volume hosts is 274.5 and that of low volume hosts is 30. The observed sample median difference in availability is 274.5 - 30.0 = 244.5.

Conducting hypothesis test:

```{r hypo-hostvolume}
set.seed(111519)
hypo_host_volume_listings <- abnb_host_volume %>%
  specify(response =  availability_365, 
          explanatory = host_volume) %>%
  hypothesize(null ="independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians",
            order = c("high volume", "low volume"))
```

The null distribution is visualized below:

```{r vis-hypo-hostvolume}
visualise(hypo_host_volume_listings) +
 labs(title = "Null distribution of differences in medians",
 subtitle = "sampmed_highvolume - sampmed_lowvolume") +
  shade_p_value(obs_stat = 244.5, 
                direction = "two_sided")
```

```{r hypo-host-volume-p-value}
get_p_value(hypo_host_volume_listings, 244.5, direction = "two_sided")
```

From the visualization, there appears to be no overlap between the shaded region and the null distribution. We found the p-value and as expected, the p-value is 0, which is less than the significance value of 0.05. Therefore, we reject the null hypothesis that there is no difference in median availability. This means that there is sufficient evidence that there is a difference in the median availability of high volume hosts and low volume hosts. Thus, to estimate the difference we construct a bootstrap simulation and find the 95% confidence interval.

Finally we construct a 95% confidence interval to find the difference in median availability:

```{r boot-hostvolume}
set.seed(111519)
boot_hostvolume <- abnb_host_volume %>%
  specify(response = availability_365,
          explanatory = host_volume) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in medians", 
            order = c("high volume", "low volume"))
```

```{r ci-boot-hostvolume}
(cibounds1 <- get_ci(boot_hostvolume, level = 0.95))
```

We are 95% confident that the median availability for high volume hosts is between 219 to 261.025 days greater than that of low volume hosts.



## Overall Conclusion

### Conclusion for Part I

Based on our research question from our proposal, we wanted to determine how location played a role in determining the price of Airbnbs in New York City. First, we summarized the sample statistics of the boroughs in New York City such as median price and number of listings to get a basic understanding of the count and distribution of price in relation to borough. After finding out that both Manhattan and Brooklyn dominated the Airbnb scene in terms of number of listings, we wanted to see how these two locations play a role in the price of Airbnbs. We predicted that Manhattan would have a higher true median price than Brooklyn because Manhattan is known from previous knowledge to be a higher-class neighborhood. So, we conducted a hypothesis test to determine if there is a true median price difference between these two boroughs. We concluded that there was sufficent evidence that Manhattan's median price is higher than Brooklyn's median price. After conducting a confidence interval for the different in true median price, we are 95% confident that the median price in Manhattan is between $55 and $65 higher than the median price in Brooklyn. We also performed linear regression to create a linear model that describes how boroughs influence price. However, before we performed our linear regression, we had to make assumptions: independence and constant variance. We could safely assume independence because we do not suspect hosts are colluding to price fix listings. However, upon performing constant variance tests, we discovered that our residual plots do not follow the form of constant variance. Therefore, we proceeded with caution. We then created a new variable called "price_case" which is a catagorical variable which indicated whether the price is at or above the median price of a listing. We then used this new variable to create a scatterplot map with color indicating median price to see how coordinates play a role in the price of Airbnbs. We concluded that Manhattan has the greatest frequency of median or above listings at 68.757%, followed by Brooklyn at 40.380%. Queens has 24.448%, Staten Island has 21.739% and the Bronx has 15.294%. Finally, we investigated last variable corresponding to location: neighbourhood. Looking into the top ten median priced neighborhoods for Airbnb's we surprisngly found that the Bronx contains the neighborhood, Eastchester, with the highest median price of $475.00.

### Conclusion For Part II

Based on our second research question in our proposal, we wanted to see how the way in which a property is listed influences the availability of a listing. Assuming availibility is a good predictor of desirability (more availible, less desireable), we looked at how the variable “room type” affects the availability of the listing. We hypothesized that room type would be a major factor in predicting availability because our exploratory analysis showed that a shared room is likely the least desired due to the largest IQR and highest median availability of the three room types. Through our text analysis of the descriptions we found words associated with private were highly sought after. "Private" and "apartment" were highly common, indicating a private enclave, and "bedroom" indicating one's private space. In additon, our linear model predicting availability by all variables regarding listing, showed room type to be a relevant predictor. Furthermore, we decided to conduct a hypothesis test to see if availability can be explained depending on whether a host is high volume or not, where high volume indicated that a host had more than one listing, and low volume indicated a host had only one histing. We had convincing evidence to conclude that there is a difference in median availability of high volume hosts and low volume hosts. Finally, we conducted a 95% confidence interval to find the different in median availability.


### Areas of Improvement

Perhaps one of the biggest concerns among our dataset was that we could not prove constant variance. When plotting the individual error against the predicted value, the variance of the error predicted value should be constant. Graphically,this means the spread of the points around the regression line is too variable. Therefore, we had to proceed with caution when drawing assumptions from the linear regression. However, if we limit our conclusions to predictions, the consequences of a weak or not constant variance are less pressing.

Furthermore, we assumed independence in our sample, implying that each listing is independent because the pricing of one space does not directly influence the other. While some might argue there is dependence between listings to some extent, the market for Airbnbs in NYC is free and competitive, so renters, ideally, don't collude. In other words, it can be safely assumed that hosts of Airbnbs are working not together to price fix listings in New York City. 

Another critical concern to consider in our analysis are the probabilities of type 1 and type 2 errors. For the entirety of our analysis, we set our alpha level to 0.05. However, we could have set the alpha level lower to reduce type 1 error, but consequently, increased the type 2 error. It is important to consider the needs when it comes to analyzing the data. If someone wants to determine, for instance, which borough is cheaper to book an Airbnb, Manhattan or Brooklyn, they would have to set the predetermined alpha level on their desired outcome. A type 1 error would mean a false positive - that there is a true difference in median prices when there actually is not. A type 2 error is a false negative, for example, if we had concluded that there is no true difference in median prices when one exists. In order to decrease the possibility of these errors, we could increase the sample size of our data analysis. Our analysis could be stronger if we took into account the purposes that people will use it for.

If we were going to continue to work on the project, we could delve deeper into locations such as specific neighborhoods. This would allow users of our analysis to investigate further, more specifically, the cheapest places in New York City. For example, although the Bronx is one of the more affordable boroughs in our analysis, the most expensive neighborhood in our sample is in the Bronx. For travelers on a very tight budget, they may be misled by the information presented in our dataset because we were not specific enough with the location. 

### Final Thoughts


### Overall